Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-08-28 paper/paper.tex
added some plots to the paper and altered pretty much every plot in the paper Tested everything on quipu.

\section{Comparison of Mannik's Experimental and Our Stadium Shapes}
We have inspected movies made
We have found that the deterministic simulations of the protein
reaction sequence discussed above results in robust oscillatory
behavoir of polar selection and oscillation in a wide variety of cell
shapes.  This differs with Mannik's experimental findings that show
much less regular behavoir, with a large variation in the location of
maxima.  On the other hand, our stochastic simulations show irregular
behavoir in the irregular shapes and more regular, pole to pole
oscillations in the pill and stadium shaped cells.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-520}
  \caption{Arrow plots of our stadium shape}
  \label{stadium-arrow}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/NflD-time-map}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/NflD-time-map}
  \caption{Time map plots of our randst shape}
  \label{time-maps-randst}
\end{figure}

>>>>

\section{Comparison of Mannik's Experimental and Our Stadium Shapes}
We have made and studied movies that show the change in concentration
of MinD over time We have found that the deterministic simulations of
the protein reaction sequence discussed above results in robust
oscillatory behavoir of polar selection and oscillation in a wide
variety of cell shapes.  This differs with Mannik's experimental
findings that show much less regular behavoir, with a large variation
in the location of maxima.  On the other hand, our stochastic
simulations show irregular behavoir in the irregular shapes and more
regular, pole to pole oscillations in the pill and stadium shaped
cells.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-2000}
  \caption{Arrow plots of our stadium shape}
  \label{stadium-arrow}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-2000}
  \caption{Arrow plots of our pill shape}
  \label{pill-arrow}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/box-plot_D}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-exact/plots/box-plot_D}
  \caption{box plots of Mannik's shapes}
  \label{box-mannik}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/box-plot_D}
  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-exact/plots/box-plot_D}
  \caption{box plots of stadium shape}
  \label{box-stadium}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/NflD-time-map}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/NflD-time-map}
  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/NflD-time-map}
  \caption{Time map plots of our randst shape}
  \label{time-maps-randst}
\end{figure}
